# Parts

You can add parts to organize one or more book chapters together. Parts can be inserted at the top of an .Rmd file, before the first-level chapter heading in that same file. 

Add a numbered part: `# (PART) Act one {-}` (followed by `# A chapter`)

Add an unnumbered part: `# (PART\*) Act one {-}` (followed by `# A chapter`)

Add an appendix as a special kind of un-numbered part: `# (APPENDIX) Other stuff {-}` (followed by `# A chapter`). Chapters in an appendix are prepended with letters instead of numbers.



```{r}
library(psych)
library(matrixcalc)
# library(matlib)
library(pracma)
library(zoo)
library(lubridate)
library(dplyr)
library(ggplot2)
library(plotly)
```

```{r}
nss_yield <- function(n_years, beta0, beta1, beta2, beta3, tau1, tau2) {
  beta0 + 
    beta1 * (1 - exp(-n_years / tau1)) / (n_years / tau1)  + 
    beta2 * ( ( (1 - exp(-n_years / tau1)) / (n_years / tau1) ) - exp(-n_years / tau1) ) +
    beta3 * ( ( (1 - exp(-n_years / tau2)) / (n_years / tau2) ) - exp(-n_years / tau2) ) 
}
```


```{r}
nber <- vroom::vroom(
  "data/recession-nber.csv",
  col_types = list(
    date = "date",
    nber = "i"
))
# nber

gdpjh <- vroom::vroom(
  "data/recession-gdp.csv",
  col_types = c(
    date = "date",
    gdp_jh = "i"
  )
)

recsn <- inner_join(nber, gdpjh, by = "date") %>% 
  tidyr::pivot_longer(
    cols = c(nber, gdp_jh),
    names_to = "src",
    values_to = "recession",
  )
  # mutate(recession = as.factor(recession))
# recsn


# file = read.csv("data/gsw_ns_params.csv", header=TRUE) %>% 
#   na.omit() %>% 
#   filter(Date >= "1969-01-01") 
# 
# attach(file)



```


```{r}
file <- Quandl::Quandl("FED/PARAMS") %>% 
  as_tibble(.) %>% 
  # filter(Date >= "1969-01-01")
  tidyr::drop_na(.)
  # filter(Date >= "1989-01-01") 

# attach(file)

n_maturities = 120
```





```{r}
# file %>% 
  # janitor::clean_names() %>% 
  # filter(date >= "1972-01-01") 
  # filter(tau2 < 0) %>% 
  # tail
```



```{r}
# set.seed(123)


# yield = matrix(rep(0,nrow(file)*n_maturities),nrow(file),n_maturities)
# 
# for(n in 1:n_maturities)
# {
#   k =n/12
#   yield[,n]= BETA0 +BETA1*(1-exp(-k/TAU1))/(k/TAU1)+ BETA2*((1 -exp(-k/TAU1))/(k/TAU1) - exp(-k/TAU1))+ BETA3*((1-exp(-k/TAU2))/(k/TAU2)-exp(-k/TAU2))
# 
# }
# yield = yield/100
# yield_raw=as.data.frame(yield)

# yield_raw
```


```{r}
# tidyr::expand_grid(term=1:120, nss)
```


```{r}
yield_long <- file %>% 
  janitor::clean_names() %>% 
  # mutate(ym_ = lubridate::make_date(year = lubridate::year(date), month = lubridate::month(date))) %>%
  # group_by(ym_) %>%
  # filter(date == max(date)) %>% 
  # ungroup() %>% 
  # select(-ym_) %>% 
  tidyr::expand_grid(., term=1:n_maturities) %>% 
  mutate(n_years = term/12) %>% 
  mutate(yield =  ( beta0 + 
    beta1 * (1 - exp(-n_years / tau1)) / (n_years / tau1)  + 
    beta2 * ( ( (1 - exp(-n_years / tau1)) / (n_years / tau1) ) - exp(-n_years / tau1) ) +
    beta3 * ( ( (1 - exp(-n_years / tau2)) / (n_years / tau2) ) - exp(-n_years / tau2) ) )  / 100 )
# yield_long
```


```{r}
yield_m0 <- 
  yield_long %>% 
  select(date, term, yield) %>% 
  tidyr::pivot_wider(
    names_from = term,
    values_from = yield,
    names_prefix = "m_"
  ) 
# yield_m0
```






```{r}
# yield_m0 <- yield_raw %>% 
#   as_tibble(.) %>% 
#   mutate(Date = lubridate::ymd(file$Date)) %>% 
#   select(Date, starts_with("V")) %>% 
#   mutate(ym_ = lubridate::make_date(year = lubridate::year(Date), month = lubridate::month(Date))) %>%
#   group_by(ym_) %>%
#   filter(Date == max(Date)) %>% 
#   ungroup() %>% 
#   select(-ym_)
  

yield_m <- yield_m0 %>% 
  select(-date) %>% 
  as.matrix(.)
# dim(yield_m)
```




```{r}
# Use excess returns at these maturities to estimate the model.
rx_maturities = c(6,18,24,36,48,60,84,120)
# rx_maturities = c(1,2,3,4,6,12,18,24,36,48,60,84,120)
ttm = c(1:n_maturities)*(1/12)
logPrices = matrix(rep(0,nrow(yield_m)*n_maturities),nrow(yield_m),n_maturities)
for(i in 1 :n_maturities)
{
  logPrices[,i] = -1*yield_m[,i]*ttm[i]
}
rf =  -1*logPrices[(1:nrow(logPrices)-1),1]
rx =  logPrices[2:nrow(logPrices), 1:(ncol(logPrices)-1)] - logPrices[1:(nrow(logPrices)-1), 2:(ncol(logPrices))] -rf

# Principal component
K=5
yield =yield_m[,1:n_maturities]
demeanedyield = matrix(rep(0,nrow(yield)*ncol(yield)),nrow(yield),ncol(yield))
for(i in 1:ncol(yield))
{
  demeanedyield[,i]= yield[,i]-mean(yield[,i])
}
k = prcomp((demeanedyield))
yieldPCs = demeanedyield %*% (k$rotation)
x = t(yieldPCs[1:nrow(yieldPCs),1:K])

x_lhs=  x[,(2:ncol(x))]
x_rhs =  x[,(1:(ncol(x)-1))]
var_coeffs = x_lhs %*% t(x_rhs)%*%solve(x_rhs%*%t(x_rhs))
phi = var_coeffs[,1:ncol(var_coeffs)]
v = x_lhs - var_coeffs %*% x_rhs
Sigma =  v %*% t(v)/ncol(v)

# Step 2
selected_rx = t(rx[,(rx_maturities-1)])
N = nrow(selected_rx)
Z = rbind((rep(1,(nrow(yield)-1))),v,x[,1:(ncol(x)-1)])
abc = selected_rx %*% t(Z)%*%solve(Z%*%t(Z))
E = selected_rx - abc %*% Z

sigmasq_ret = tr(E %*% t(E)) / (ncol(E)*nrow(E))
h =  x[, 1:(ncol(x)-1)]
a = abc[,1]
beta = t(abc[, 1:K+1])
c = abc[, (K+2): ncol(abc)]
l = K*K
# Step(3)
Bstar = t(matrix(rep(0,N*l),N,l))
for(i in 1:ncol(Bstar))
{
  Bstar[,i]= vec(beta[,i]%*%t(beta[,i]))
}

lambda0 = solve(beta%*%t(beta))%*%beta%*%(a +0.5*(t(Bstar) %*% vec(Sigma) + sigmasq_ret * rep(1,N)))
lambda1  = solve(beta%*%t(beta))%*% beta%*%c

# Run Bond Pricing recursion
A = rep(0,n_maturities)
B = matrix(rep(0,n_maturities),K,n_maturities)
mat =rbind(rep(1,ncol(v)),x[,2:(ncol(x))])
delta = t(rf)%*%t(mat) %*% solve(mat%*%t(mat))
delta0 = delta[1]
delta1 = delta[,2:ncol(delta)]
A[1]=   0.5*(sigmasq_ret)-delta0
B[,1] = -t(delta1)
for(i in 2:(n_maturities))
{
  A[i] = A[i-1]+ t(B[,i-1])%*%(-lambda0) +0.5*(t(B[,i-1])%*% Sigma %*% B[,i-1]+ sigmasq_ret)-delta0
  B[,i] = t(B[,i-1])%*%(phi-lambda1)-t(delta1)
}

# Construct fitted yields
fittedLogPrices = t(t(B)%*%x)
fittedYields = t(t(B)%*%x)
for(i in 1: n_maturities)
  fittedLogPrices[,i] = fittedLogPrices[,i] +A[i]
for(i in 1: n_maturities)
  fittedYields[,i] =  t((fittedLogPrices[,i]/ttm[i])*(-1))

#Construct risk free yields
A = rep(0,(n_maturities))
B = matrix(rep(0,(n_maturities)),K,(n_maturities))
A[1]= 0.5*(sigmasq_ret)-delta0
B[,1] = -t(delta1)

for(i in 2:(n_maturities))
{
  A[i] = A[i-1]+0.5*(t(B[,i-1])%*% Sigma %*% B[,i-1]+ sigmasq_ret)-delta0
  B[,i] = t(B[,i-1])%*%(phi)-t(delta1)
}

# Construct risk free yields
RiskfreeLogPrices = t(t(B)%*%x)
RiskfreeYields = t(t(B)%*%x)
for(i in 1: n_maturities)
  RiskfreeLogPrices[,i] = RiskfreeLogPrices[,i] +A[i]
for(i in 1: n_maturities)
  RiskfreeYields[,i] =  t((RiskfreeLogPrices[,i]/ttm[i])*(-1))

termpremium = fittedYields - RiskfreeYields

```



```{r}
colnames(yield_m) <- paste(rep("m", n_maturities), 1:n_maturities, sep = "_")
colnames(termpremium) <- paste(rep("m", n_maturities), 1:n_maturities, sep = "_")
```



```{r}
  # termpremium %>% 
  # as_tibble(.)  %>% 
  # mutate(Date = yield_m0$date) %>% 
  # tidyr::pivot_longer(
  #   cols = -Date,
  #   names_to = "term",
  #   values_to = "premium",
  #   names_prefix = "m_"
  # )
```


```{r}
# yield_m0 %>% 
#   as_tibble(.)  %>%
#   mutate(Date = yield_m0$date) %>%
#   select(-date) %>% 
  # tidyr::pivot_longer(
  #   cols = -Date,
  #   names_to = "term",
  #   values_to = "yield",
  #   names_prefix = "m_"
  # )
```



```{r}
yp <- inner_join(
  yield_m0 %>%
  # as_tibble(.)  %>%
  mutate(Date = yield_m0$date) %>%
  select(-date) %>%
  tidyr::pivot_longer(
    cols = -Date,
    names_to = "term",
    values_to = "yield",
    names_prefix = "m_"
  ),
  termpremium %>%
  as_tibble(.)  %>%
  mutate(Date = yield_m0$date) %>%
  tidyr::pivot_longer(
    cols = -Date,
    names_to = "term",
    values_to = "premium",
    names_prefix = "m_"
  ),
  by = c("Date", "term")
) %>%
  mutate(
    # date = lubridate::floor_date(lubridate::ymd(Date), "month"),
    date = Date,
    term = as.integer(term)) %>%
  select(date, term, yield, premium)
# yp
```






```{r}
yp %>% 
  filter(date == "2023-02-28" & term == 120)
```


```{r}
date_ <- yp %>% summarise(date_ = max(date)) %>% pull(date_)

yp %>% 
  filter(date == max(date)) %>% 
  ggplot(aes(term, premium)) +
  geom_path() +
  labs(title=stringr::str_interp("US Treasuries ${date_}"))
```


```{r}
date_ <- yp %>% summarise(date_ = max(date)) %>% pull(date_)

yp %>% 
  filter(date == max(date)) %>% 
  ggplot(aes(term, premium)) +
  geom_path() +
  labs(title=stringr::str_interp("US Treasuries ${date_}"))
```



```{r}
yp %>%
  mutate(date = as.factor(date)) %>% 
  plot_ly(
    x = ~term,
    y = ~premium,
    frame = ~date,
    type = "scatter",
    mode = "markers",
    hoverinfo = "text"
  ) %>%
  layout(yaxis = list(title="premium",range=c(-.02, .05)), xaxis = list(title="term (months)"))
```



```{r}
# df <- left_join(
#   yp, recsn,
#   by = "date"
# ) %>% 
  # group_by(src) %>% 
  # mutate(recession = tidyr::fill(recession))
  # tidyr::fill(recession) %>% 
  # ungroup() %>% 
  # filter(date == "1969-02-01")
  # filter(date >= "1990-01-01") %>%
  # mutate(y = lubridate::year(date), m= stringr::str_pad(lubridate::month(date),2,pad="0")) %>% 
  # mutate(date = stringr::str_c(y,m,sep="-")) %>% 
  # mutate(date = as.factor(date)) %>%
  # mutate(recession = as.factor(if_else(recession == 1, "recession", "fine"))) %>%
  # select(date, term, yield, premium, src, recession)
# df
```

```{r}
# df_nber <- df %>% filter(src == "nber")
# df_gdpjh <- df %>% filter(src == "gdp_jh")
```

```{r}
# df %>% summarise(max(premium), min(premium))
```




```{r}
# fig_p_nber <-
#   df_nber %>%
#   plot_ly(
#     x = ~term,
#     y = ~premium,
#     frame = ~date,
#     color = ~recession,
#     type = "scatter",
#     mode = "markers",
#     hoverinfo = "text"
#   ) %>%
#   layout(yaxis = list(title="premium",range=c(-.02, .05)), xaxis = list(title="term (months)"))
# 
# 
# fig_p_gdpjh <- 
#   df_gdpjh %>% 
#   plot_ly(
#     x = ~term,
#     y = ~premium,
#     frame = ~date,
#     color = ~recession,
#     type = "scatter",
#     mode = "markers",
#     hoverinfo = "text"
#   ) %>% 
#   layout(yaxis = list(title="premium", range=c(-.02, .05)), xaxis = list(title="term (months)"))
# 
# 
# 
# fig <- subplot(
#   fig_p_nber, fig_p_gdpjh, 
#   nrows = 2,
#   titleY = TRUE,
#   titleX = TRUE,
#   shareX = TRUE,
#   margin = 0.1
#   ) %>% 
#   layout(
#     title = "Treasuries and Recession Relationship",
#     # yaxis = list(range=c(-.02, .05)),
#     legend =list(title=list(text="<b> Recession? </b>")),
#     annotations = list( 
# 
#   list( 
# 
#     x = 0.2,  
# 
#     y = 1.0,  
# 
#     text = "NBER",  
# 
#     xref = "paper",  
# 
#     yref = "paper",  
# 
#     xanchor = "center",  
# 
#     yanchor = "bottom",  
# 
#     showarrow = FALSE 
# 
#   ),  
# 
# 
#   list( 
# 
#     x = 0.2,  
# 
#     y = 0.4,  
# 
#     text = "GDP",  
# 
#     xref = "paper",  
# 
#     yref = "paper",  
# 
#     xanchor = "center",  
# 
#     yanchor = "bottom",  
# 
#     showarrow = FALSE 
# 
#   ))
#     )
#   
# fig
```




```{r}
# fig_p_nber <- 
#   df_nber %>% 
#   plot_ly(
#     x = ~term,
#     y = ~premium,
#     frame = ~date,
#     color = ~recession,
#     type = "scatter",
#     mode = "markers",
#     hoverinfo = "text"
#   ) %>% 
#   layout(yaxis = list(title="premium"), xaxis = list(title="term (months)"))
# 
# fig_y_nber <- 
#   df_nber %>% 
#   plot_ly(
#     x = ~term,
#     y = ~yield,
#     frame = ~date,
#     color = ~recession,
#     type = "scatter",
#     mode = "markers",
#     hoverinfo = "text"
#   ) %>% 
#   layout(yaxis = list(title="yield"), xaxis = list(title="term (months)")) 
# 
# fig_p_gdpjh <- 
#   df_gdpjh %>% 
#   plot_ly(
#     x = ~term,
#     y = ~premium,
#     frame = ~date,
#     color = ~recession,
#     type = "scatter",
#     mode = "markers",
#     hoverinfo = "text"
#   ) %>% 
#   layout(yaxis = list(title="premium"), xaxis = list(title="term (months)"))
# 
# fig_y_gdpjh <- 
#   df_gdpjh %>% 
#   plot_ly(
#     x = ~term,
#     y = ~yield,
#     frame = ~date,
#     color = ~recession,
#     type = "scatter",
#     mode = "markers",
#     hoverinfo = "text"
#   ) %>% 
#   layout(yaxis = list(title="yield"), xaxis = list(title="term (months)"))
# 
# fig <- subplot(
#   fig_p_nber, fig_y_nber, fig_p_gdpjh, fig_y_gdpjh, 
#   nrows = 2,
#   titleY = TRUE,
#   titleX = TRUE,
#   # shareX = TRUE,
#   margin = 0.1
#   ) %>% 
#   layout(
#     title = "Treasuries and Recession Relationship",
#     legend =list(title=list(text="<b> Recession? </b>")),
#     annotations = list( 
# 
#   list( 
# 
#     x = 0.2,  
# 
#     y = 1.0,  
# 
#     text = "NBER",  
# 
#     xref = "paper",  
# 
#     yref = "paper",  
# 
#     xanchor = "center",  
# 
#     yanchor = "bottom",  
# 
#     showarrow = FALSE 
# 
#   ),  
# 
#   list( 
# 
#     x = 0.8,  
# 
#     y = 1,  
# 
#     text = "NBER",  
# 
#     xref = "paper",  
# 
#     yref = "paper",  
# 
#     xanchor = "center",  
# 
#     yanchor = "bottom",  
# 
#     showarrow = FALSE 
# 
#   ),  
# 
#   list( 
# 
#     x = 0.2,  
# 
#     y = 0.4,  
# 
#     text = "GDP",  
# 
#     xref = "paper",  
# 
#     yref = "paper",  
# 
#     xanchor = "center",  
# 
#     yanchor = "bottom",  
# 
#     showarrow = FALSE 
# 
#   ),
# 
#   list( 
# 
#     x = 0.8,  
# 
#     y = 0.4,  
# 
#     text = "GDP",  
# 
#     xref = "paper",  
# 
#     yref = "paper",  
# 
#     xanchor = "center",  
# 
#     yanchor = "bottom",  
# 
#     showarrow = FALSE 
# 
#   ))
#     )
#   
# fig
```


```{r}
# yp %>% 
#   filter(date == max(date)) %>% 
#   ggplot(aes(term, premium)) +
#   geom_line() +
#   labs(title = "March")
```





```{r}
# termpremium %>%
  # as_tibble(.) 
  # tidyr::pivot_longer(
  #   cols = -dt,
  #   names_to = "term",
  #   values_to = "premium",
  #   names_prefix = "V"
  # ) %>%
  # mutate(term = as.integer(term)) %>%
  # filter(dt == "2023-03-17") %>%
  # # filter(premium > 0)
  # ggplot(aes(term, premium)) +
  # geom_line()
```






