# Footnotes and citations 

## Footnotes

Footnotes are put inside the square brackets after a caret `^[]`. Like this one ^[This is a footnote.]. 

## Citations

Reference items in your bibliography file(s) using `@key`.

For example, we are using the **bookdown** package [@R-bookdown] (check out the last code chunk in index.Rmd to see how this citation key was added) in this sample book, which was built on top of R Markdown and **knitr** [@xie2015] (this citation was added manually in an external file book.bib). 
Note that the `.bib` files need to be listed in the index.Rmd with the YAML `bibliography` key.


The RStudio Visual Markdown Editor can also make it easier to insert citations: <https://rstudio.github.io/visual-markdown-editing/#/citations>


```{r}
# kwo0 <- vroom::vroom(
#   "data/feds200533.csv",
#   delim = "\n"
# )
# kwo0
```

```{r}
# kwo <- kwo0[9:nrow(kwo0),]
# colnames(kwo) <- kwo0[8,]
```

```{r}
# kwo1 <- kwo0[8:nrow(kwo0),]
# colnames(kwo1) <- NULL

```


```{r}

# kwo1[[1]] %>% 
  # glue::glue("\n")
  # paste0("\n")
```


```{r}
# kwo[[1]] %>% paste0(.,"\n") %>% vroom::vroom()
```


```{r}
# kwo1[[1]] %>% 
#   paste0(., "\n") %>% 
#   vroom::vroom(., delim=",") %>% 
#   janitor::clean_names()
```
